---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fipio

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/fipio)](https://CRAN.R-project.org/package=fipio)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/fipio)](https://CRAN.R-project.org/package=fipio)
[![codecov](https://codecov.io/gh/program--/fipio/branch/master/graph/badge.svg?token=1ODDHARQM1)](https://codecov.io/gh/program--/fipio)
[![R-CMD-check](https://github.com/program--/fipio/workflows/R-CMD-check/badge.svg)](https://github.com/program--/fipio/actions)
[![MIT License](https://img.shields.io/badge/license-MIT-blue.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

`fipio` is a **lightweight** package that makes it easy to get information about a US FIP code.

## Installation

You can install the released version of `fipio` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fipio")
```

or the development version with `pak` or `remotes`:
``` r
# Using `pak`
pak::pkg_install("program--/fipio")

# Using `remotes`
remotes::install_github("program--/fipio")
```

## Usage

`fipio` makes it easy to get information about a US FIP code.
Let's answer a few questions that might come up if you have a FIP code:

```{r}
fip <- "37129"

# What state is `37129` in?
fipio::state(fip)

# Alternatively, you can use the state FIP code by itself
fipio::state("37")

# What about the state abbreviation?
fipio::abbr(fip)

# What county is `37129`?
fipio::county(fip)

# It'd be nice to have this all in a data.frame...
fipio::metadata(fip)

# And the metadata for the state by itself...
fipio::metadata("37")
```

### With `sf`
`fipio` also includes functions that support geometry for FIP codes. This requires
`sfheaders` at the very least to get an `sf`-compatible geometry object back.

```{r, include = FALSE}
library(sf, quietly = TRUE)
```

```{r}
# I'm doing spatial work, what's the geometry of `37129`?
fipio::geometry(fip)

# What if I need it with my other metadata?
fipio::metadata(fip, geometry = TRUE)
```

### Vectorized
`fipio` functions are inherently vectorized, so you can use them with vectors of FIP codes easily:
```{r}
fips <- c("37129", "44001", "48115")

fipio::state(fips)

fipio::abbr(fips)

fipio::county(fips)

fipio::metadata(fips)

fipio::geometry(fips)
```